---
title: "Rates and Trends"
output: html_notebook
runtime: shiny
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)
library(broom)
library(lme4)

```

#Introduction
This note is intended to help with interpreting the results of experiments that are designed to compare rates or trends. Data is first simulated, before being modelled using linear regression.

#Shared parameters

```{r}
inputPanel(
  
  numericInput("n_points", label = "Number of time points:",
              value = 6),
  numericInput("m_points", label = "Number of measurements per time point:",
              value = 5),
  numericInput("sd", label = "Standard deviation of measurements:",
              value = 0.1)
  
)
```

#Case specific parameters

```{r}
inputPanel(

  numericInput("rate_A", label = "Rate of case A (r):",
              value = -0.3),
  
  numericInput("intercept_A", label = "Intercept of case A (s):",
              value = 20)
)

inputPanel(
  numericInput("rate_B", label = "Rate of case B (r):",
              value = -0.5),
  
  numericInput("intercept_B", label = "Intercept of case B (s):",
              value = 20)
)


```

```{r}

#Simulate data
simulation<-reactive({
  
  relationship<-function(t,rate,intercept){
    #return(intercept+(rate*t)) #linear relationship
    return(intercept*(10^(rate*t))) #power 10 relationship
  }
  
  mn=input$m_points*input$n_points
  
  set.seed(input$random_seed)
  
  time_points<-seq(0,input$n_points-1) %>%
    rep(each=input$m_points)
  
  case<-c(rep("case_A",times=mn),
           rep("case_B",times=mn))
  
  repeat_group<-c(
    LETTERS[seq(1,input$m_points)] %>%
      rep(times=input$n_points),
    LETTERS[seq(input$m_points+1,input$m_points*2)] %>%
      rep(times=input$n_points)
    )
  
  value_A<-relationship(time_points,input$rate_A,input$intercept_A)
  
  value_B<-relationship(time_points,input$rate_B,input$intercept_B)
  
  error<-rnorm(input$n_points*input$m_points*2,sd=input$sd)

  data.frame(time_points=c(time_points,time_points),
             case=case,
             repeat_group=repeat_group,
             value=c(value_A,value_B),
             error=error,
             value_error=c(value_A,value_B)+error,
             log10_value_error=log10(c(value_A,value_B)+error))
  
})


```

#Plot options

```{r}

inputPanel(

  selectInput("graph_type", "Graph type:",c("Line with errors","Scatter with trends")),
  checkboxInput("log_scale", "Log scale:", FALSE)
  
)

```

```{r}
renderPlot({
  
  plot_data<-simulation()
  
  myplot<-ggplot(plot_data,aes(x=time_points,y=value_error,colour=case))
  
  if(input$graph_type=="Line with errors"){
    #Hopefully familiar plot
    myplot<-myplot +
      stat_summary(fun.y = mean, geom = "line") + 
      stat_summary(fun.data = mean_se, geom = "errorbar")
  }
  else
  {
    #Data science style plot
    myplot<-myplot +
      geom_smooth()+
      geom_jitter(width = 0.1)
  }
  
  if(input$log_scale==TRUE){
    myplot<-myplot +
      scale_y_log10()
  }
  
  myplot
  
})
```

#Log transform

$$y=s10^{rt}$$

$$\log_{10}y=\log_{10}(s10^{rt})$$

$$\log_{10}y=\log_{10}s+rt$$

#Linear regression

```{r}

renderTable({
  
  reg_data<-simulation()
  
  reg_data %>%
    lm(formula=log10_value_error~time_points * case, data=.) %>%
    tidy(conf.int=TRUE, conf.level=0.95) %>%
    add_column("description"=c("Intercept of case A (s)",
                               "Rate of case A (r)",
                               "Difference between Intercept of case A (s) and Intercept of case B (s)",
                               "Difference between Rate of case A (r) and Rate of case B (r)")) %>%
    add_column("true.value"=c(input$intercept_A,
                              input$rate_A,
                              input$intercept_B-input$intercept_A,
                              input$rate_B-input$rate_A)) %>%
    select("term","description","true.value","conf.low","estimate","conf.high","p.value")
  
  
  #10^intercept is intercept_A
  #time_points is rate_A
  #10^(intercept-casecase_B) is intercept_B
  #time_points - time_points:casecase_B is rate_B
  
},digits=-5)

```



#Linear mixed effects
```{r}

renderPrint({
  
  reg_data<-simulation()
  
  reg_data %>%
      lmer(formula=log10_value_error~time_points * case + (1|repeat_group), data=.) 
  
})

```

#Randomisation
When all parameters including the random seed are kept the same, the simulation results will be the same. This means we can go back to exactly the same simulated data, by remembering the random seed. If we want to re-simulate the data with the rest of the parameters kept constant, the seed can be changed.
```{r}
inputPanel(
  
  numericInput("random_seed", label = "Random seed:",
              value = 1, step = 1)
  
)
```


```{r}

renderTable({
  
  #simulation()

},digits = 5)
```

